### 2017-10-25 Draft2/Appending.Dynamic.tex
Labels
Get the theorems straight?

I will first implement appending for dynamic arrays. Let $\VarList$ be a dynamic array. The following definitions are used in the code:

@@

\begin{lemma}
\label{CapacitySequence}
	Let $\VarList$ by a dynamic array. As $n$ items are appended, the sequence of capacities $\VarList$ takes on is $$S_C = 0,\ \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil}\VarInitCapacity$$.
\end{lemma}

@@

From \ref{CapacitySequence} I know the exact capacities $\VarList$ takes on as $n$ items are appended. Dynamic arrays also have the property that $i \in S_C$ iff an array of length $i$ was allocated. Then the total length of arrays allocated is

>>>>

I will implement appending for dynamic arrays first. Let $\VarList$ be a dynamic array. The following definitions are used in the code:

@@

\begin{lemma}
\label{lem:CapacitySequence}
	Let $\VarList$ by a dynamic array. As $n$ items are appended, the sequence of capacities $\VarList$ takes on is $$S_C = 0,\ \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil}\VarInitCapacity$$.
\end{lemma}

@@

From \ref{lem:CapacitySequence} I know the exact capacities $\VarList$ takes on as $n$ items are appended. Dynamic arrays also have the property that $i \in S_C$ iff an array of length $i$ was allocated. Then the total length of arrays allocated is

### 2017-10-25 Draft2/AsymptoticNotation.tex
Get the theorems straight?

\begin{align*}
f(n) \sim g(n) \leftrightarrow \lim_{n \to \infty} \frac{g(n)}{f(n)} = 1
\end{align*}

$f$ and $g$ may be used as shorthand to denote $f(n)$ and $g(n)$, respectively.

@@

A useful property $\sim$ shares with $O$ is that it merges over arithmetic operations. This is stated by the following two theorems, which are proved in \ref{pf:MergesOverArithmetic}.

@@

Another nice property $\sim$ and $O$ have in common is that lower-order terms are removed from consideration. For example, $n \sim (n + \log_2 n)$. This is stated by the below theorem, which is proved in \ref{pf:RemovesLowerOrderTerms}.

\begin{theorem}
\label{thm:RemovesLowerOrderTerms}
	If $\lim_{n \to \infty} g / f = 0$, then $f + g \sim f$.
\end{theorem}

Finally, $\sim$ is a transitive operator. That is,

@@

This property is used implicitly by proofs that chain multiple $\sim$s in the form $f \sim g \sim h$, then conclude that $f \sim h$. It is proved in \ref{pf:Transitivity}.

>>>>

\begin{align*}
f \sim g \leftrightarrow \lim_{n \to \infty} \frac{g}{f} = 1
\end{align*}

This is read as "$f$ is asymptotic to $g$" or "$f$ and $g$ are asymptotic." {\HdrNote} $f$ and $g$ are used as shorthand to denote $f(n)$ and $g(n)$, respectively.

@@

Here, I define various properties of the $\sim$ relation that will be used in my proofs. Proofs of these properties can be found in the appendix.

The following two theorems state that $\sim$ can "merge", or un-distribute, over arithmetic operations. This is a property shared with big-O.

@@

The following theorem states that lower-order terms may be removed. For example, $(n + \log_2 n) \sim n$.

\begin{theorem}
\label{thm:RemovesLowerOrderTerms}
	If $\lim_{n \to \infty} g / f = 0$, then $f + O(g) \sim f$.
\end{theorem}

The following theorem shows that $\sim$ is a transitive relation. This property is used implicitly by proofs that chain multiple $\sim$s in the form $f \sim g \sim h$, then conclude that $f \sim h$.

@@

The following theorem states that if two functions are asymptotic, then they belong to the same big-O class.

\begin{theorem}
\label{thm:SameBigOClass}
	If $f \sim g$ and $g = O(h)$, then $f = O(h)$.
\end{theorem}

### 2017-10-25 Draft2/CommonOperations.Blurb.tex
Get the theorems straight?

In this section, I implement common operations for dynamic and growth arrays, and analyze their time complexity. I also analyze space complexity of operations that allocate memory.

>>>>

In this section, I implement the most common operations for dynamic and growth arrays, then analyze their time complexity. If the operation allocates memory, I also analyze its space complexity.

### 2017-10-25 Draft2/FieldsProperties.tex
Tweak "Fields and Properties"
Get the theorems straight?

\begin{algorithm}
	\begin{algorithmic}
		\State $\VarList.\FieldBuffer \gets \FuncNewArray(0)$
		\State $\VarList.\FieldSize \gets 0$
	\end{algorithmic}
\end{algorithm}

@@

\begin{itemize}
	\item $\VarList.\FieldHead$ - The \textbf{head} of $\VarList$. It returns the buffer we are currently adding items to.
	\item $\VarList.\FieldTail$ - The \textbf{tail} of $\VarList$. It returns a dynamic array of buffers that have already been filled. This can be thought of as a two-dimensional array.
	\item $\VarList.\FieldSize$ - The number of items in $\VarList$.
	\item $\VarList.\FieldCapacity$ - The \textbf{capacity} of $\VarList$. It returns the maximum number of items $\VarList$ can hold without resizing.
\end{itemize}

@@

\begin{algorithm}
	\begin{algorithmic}
		\State $\VarList.\FieldHead \gets \FuncNewArray(0)$
		\State $\VarList.\FieldTail \gets \FuncNewDynamicArray()$
		\State $\VarList.\FieldSize \gets 0$
		\State $\VarList.\FieldCapacity \gets 0$
	\end{algorithmic}
\end{algorithm}

>>>>

\begin{algorithm}
	\begin{algorithmic}
		\Procedure{$\FuncConstructor$}{$\VarList$}
			\State $\VarList.\FieldBuffer \gets \FuncNewArray(0)$
			\State $\VarList.\FieldSize \gets 0$
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

@@

\begin{itemize}
	\item $\VarList.\FieldHead$ - The \textbf{head} of $\VarList$. It returns the buffer we are currently adding items to.
	\item $\VarList.\FieldTail$ - The \textbf{tail} of $\VarList$. It returns a dynamic array of references to buffers that have already been filled. This can be thought of as a two-dimensional array.
		\subitem It may seem strange for growth arrays to use dynamic arrays internally. There is little harm from the extra copying and allocations these dynamic arrays perform, however, since only $O(\log n)$ references are appended to them (proved in [ref3]).
	\item $\VarList.\FieldSize$ - The number of items in $\VarList$.
	\item $\VarList.\FieldCapacity$ - The \textbf{capacity} of $\VarList$. It returns the maximum number of items $\VarList$ can hold without resizing.
\end{itemize}

@@

\begin{algorithm}
	\begin{algorithmic}
		\Procedure{$\FuncConstructor$}{$\VarList$}
			\State $\VarList.\FieldHead \gets \FuncNewArray(0)$
			\State $\VarList.\FieldTail \gets \FuncNewDynamicArray()$
			\State $\VarList.\FieldSize \gets 0$
			\State $\VarList.\FieldCapacity \gets 0$
		\EndProcedure
	\end{algorithmic}
\end{algorithm}
